---
title: "Car Details"
author: "Harsh Kapadia"
date: '2022-03-26'
output: html_document
---

# Loading Data

GitHub Repository: [HarshKapadia2/car-details](https://github.com/HarshKapadia2/car-details)

## Load Data

```{r}
data <- read.csv("https://raw.githubusercontent.com/HarshKapadia2/car-details/main/data/car_details_v3.csv")
head(data)
```

## Structure of Data

```{r}
str(data)
```

## Installing Packages

```{r}
# install.packages("tidyverse", repos = "http://cran.us.r-project.org") # For `ggplot2` and `dplyr`
install.packages("ggplot2", repos = "http://cran.us.r-project.org")
install.packages("dplyr", repos = "http://cran.us.r-project.org")
# install.packages("fansi", repos = "http://cran.us.r-project.org") # To solve `tidyverse` package error
install.packages("plotrix", repos = "http://cran.us.r-project.org") # For 3d Pie Chart
library(plotrix)
library(tidyverse)
```

# Data Cleaning

## Remove Incomplete Rows

```{r}
count(data)
```

```{r}
sum(is.na(data))
row_status <- complete.cases(data)
data <- data[row_status,] # [row, column]
sum(is.na(data))
```

```{r}
count(data)
```

## Convert Engine Column from Character to Integer Vector

```{r}
str(data$engine)

engine_chr_values <- strsplit(data$engine, split = " ", fixed = TRUE)
engine_count <- length(engine_chr_values)
new_engine_values <- vector()

for (i in 1:engine_count) {
  new_engine_values[i] <- strtoi(engine_chr_values[[i]][1])
}

data$engine <- new_engine_values
str(data$engine)
```

## Convert Mileage Column from Character to Numeric Vector

```{r}
str(data$mileage)

mileage_chr_values <- strsplit(data$mileage, split = " ", fixed = TRUE)
mileage_count <- length(mileage_chr_values)
new_mileage_values <- vector()

for (i in 1:mileage_count) {
  new_mileage_values[i] <- as.numeric(mileage_chr_values[[i]][1])
}

data$mileage <- new_mileage_values
str(data$mileage)
```

## Convert Max Power Column from Character to Numeric Vector

```{r}
str(data$max_power)

max_power_chr_values <- strsplit(data$max_power, split = " ", fixed = TRUE)
max_power_count <- length(max_power_chr_values)
new_max_power_values <- vector()

for (i in 1:max_power_count) {
  new_max_power_values[i] <- as.numeric(max_power_chr_values[[i]][1])
}

data$max_power <- new_max_power_values
str(data$max_power)
```

# Visualising Data

## Histogram

```{r}
hist(data$seats, main = "No. of Seats vs No. of Cars", xlab = "No. of Seats", ylab = "No. of Cars")
```

## Box Plot

```{r}
temp_data <- data %>%
  select(selling_price, seats) %>%
  filter(selling_price < 200000)

boxplot(temp_data$selling_price ~ temp_data$seats, main = "No. of Seats vs Selling Price", xlab = "No. of Seats", ylab = "Selling Price (Rs)")
```

## Pie Chart

```{r}
fuel_count = data %>% count(fuel)
pie(fuel_count$n, labels = fuel_count$fuel, radius = 1, col = c("orange", "blue", "yellow", "dark green"), main = "Fuel Type")
```

## 3D Pie Chart

```{r}
transmission_count = data %>% count(transmission)
pie3D(transmission_count$n, labels = transmission_count$transmission, radius = 1, col = c("yellow", "blue"), explode = 0.4, main = "Transmission Type")
```

## Bar Plot

```{r}
barplot(table(data$seller_type), main = "Seller Type vs No. of Cars")
```

## Scatter Plot

```{r}
graph_data_1 <- data %>%
  select(selling_price, km_driven) %>%
  filter(selling_price < 5000000, km_driven < 400000)

ggplot(graph_data_1, aes(x = selling_price, y = km_driven)) + geom_point() + geom_smooth() + labs(title = "Selling Price vs Distance Driven", x = "Selling Price (Rs)", y = "Distance Driven (km)")
```

## Line Plot

```{r}
graph_data_2 <- data %>%
  select(selling_price, km_driven) %>%
  filter(selling_price > 2000000, km_driven < 400000)

ggplot(graph_data_2, aes(x = selling_price, y = km_driven)) +
  stat_summary(fun.y = "mean", geom = "line", size = 1, linetype = "solid") +
  labs(title = "Selling Price vs Distance Driven", x = "Selling Price (Rs)", y = "Distance Driven (km)")
```

## Bar Chart

```{r}
ggplot(data, aes(x = fuel, fill = owner)) + geom_bar() + labs(title = "Fuel Type vs No. of Cars vs Owner", x = "Fuel Type", y = "No. of Cars", fill = "Owner")
```

## Dot Plot

```{r}
ggplot(data, aes(x = seats, y = fuel)) + geom_point(col = "red", size = 5) +
  geom_segment(aes(x = min(seats), xend = max(seats), y = fuel, yend = fuel), linetype = "dashed", size = 0.1) +
  labs(title = "No. of Seats vs Fuel Type", x = "No. of Seats", y = "Fuel Type")
```

## Smooth Plot

```{r}
graph_data <- data %>%
  select(mileage, engine)

ggplot(graph_data, aes(x = engine, y = mileage)) + geom_smooth() + labs(title = "Engine Capacity vs Car Mileage", x = "Engine Capacity (cc)", y = "Car Mileage (km/L)")
```

## Density Plot

```{r}
ggplot(data, aes(mileage)) + geom_density(aes(fill = fuel), alpha = 0.3) + labs(title = "Car Mileage vs Density vs Fuel Type", x = "Car Mileage (km/L)", y = "Density", fill = "Fuel Type")
```
